FocalGstar

### 2017-06-15 analysis.Rmd
minor code refactoring

```{r setup, echo=FALSE, message=FALSE}
library(dplyr)
library(knitr)
library(rgdal)
library(readr)
library(corrplot)

@@

@@

  g <- GetisOrd(r, w, st)
  plot_zscore(g,
              title = sprintf("Focal G*: wsize=%d", ws),
              sigma_thresh = 2)
  writeRaster(g,
              sprintf("data/blur/focalgstar-%dx%d-z%02d-w%02d.tif",
                      nrow(r), ncol(r), ZOOMLEVEL, ws),
              overwrite = TRUE)
}
```
## Parent-Child Clumping Difference
```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
r <- rast[[ZOOMLEVEL]]
st1 <- GetisOrdStandardStats(r)
st2 <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
plot_clumping_diff(r, st1, ZOOM_WMATRIX_SIZE, 29)
plot_clumping_diff(r, st2, ZOOM_WMATRIX_SIZE, 29)
```

## Eval SoH-up
```{r, eval=FALSE}
# expand.grid(
#   zoom = seq_along(rast),
#   wsize = wsizes,
#   soh = NA
# ) ->
#   soh_up_gstar ->
#   soh_up_focalgstar ->
#   soh_down_gstar ->
#   soh_down_focalgstar

# zooms <- 5:length(rast)

# pbmax <- length(wsizes) * length(zooms)
# pbidx <- 0
# pb <- txtProgressBar(max = pbmax, style = 3)

# wgen <- function(ws) {
#   w <- weight_matrix_circular_fade(ws, 0)
#   w[is.na(w)] <- 0 # removing any NAs from the weight matrix
#   w
# }
# 
# results <- matrix(nrow = 0, ncol = 4)
# colnames(results) <- c("zoom",
#                        "wm size",
#                        "soh_up(G*)",
#                        "soh_up(Focal G*)")
# 
# for (zoom in zooms) {
#   
#   r <- rast[[zoom]]
#   st_std <- GetisOrdStandardStats(r)
#   st_foc <- GetisOrdLocalStats(r, weight_matrix_circular(51))
#   
#   std_up <- eval_getisord(r, st_std, wsizes, wgen = wgen)
#   foc_up <- eval_getisord(r, st_foc, wsizes, wgen = wgen)
#   
#   results <- rbind(results, cbind(zoom, wsizes[-1], std_up[,2], foc_up[,2]))

  # plot(res_std, type = "n", ylim = c(0,1))
  # lines(res_std, col = "red")
  # lines(res_foc, col = "blue")

  # for (ws in wsizes) {
  #   w <- weight_matrix_circular_fade(ws, 0)
  #   w[is.na(w)] <- 0 # removing any NAs from the weight matrix
  #   
  #   
  #   pbidx <- pbidx + 1
  #   setTxtProgressBar(pb, pbidx)
  # }
# }
# close(pb)
```

@@

```{r, eval=FALSE}
foc %>%
  cor(use = "pairwise.complete.obs") %>%
  corrplot.mixed(order = "FPC", diag = "n", outline = "gray")
```

@@

zoom_soh %>% dplyr::select(Zoom, "G*" = UpZoomGstar) -> y1
zoom_soh %>% dplyr::select(Zoom, "Focal G*" = UpFocalGstar) -> y2

@@

zoom_soh %>% dplyr::select(Zoom, "G*" = DownZoomGstar) -> y1
zoom_soh %>% dplyr::select(Zoom, "Focal G*" = DownZoomFocalGstar) -> y2

@@

>>>>

```{r setup, echo=FALSE, message=FALSE}
library(dplyr)
library(knitr)
library(rgdal)
library(readr)
library(corrplot)
library(plotrix)

@@

```{r blur-wmatrices, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
for(ws in wsizes) {
  w <- weight_matrix_circular_fade(ws, 0)
  w[is.na(w)] <- 0 # removing any NAs from the weight matrix
  plot_weight_matrix(w)
}
```

@@

  g <- GetisOrd(r, w, st)
  plot_zscore(g,
              title = sprintf("Focal G*: wsize=%d", ws),
              sigma_thresh = 2)
  writeRaster(g,
              sprintf("data/blur/focalgstar-%dx%d-z%02d-w%02d.tif",
                      nrow(r), ncol(r), ZOOMLEVEL, ws),
              overwrite = TRUE)
}
```
## Example of Parent-Child Clumping Difference
```{r metric-example, message=FALSE, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
r <- rast[[ZOOMLEVEL]]
st1 <- GetisOrdStandardStats(r)
st2 <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
plot_clumping_diff(r, st1, ZOOM_WMATRIX_SIZE, 29)
plot_clumping_diff(r, st2, ZOOM_WMATRIX_SIZE, 29)
```

@@

```{r, eval=FALSE, echo=FALSE}
foc %>%
  cor(use = "pairwise.complete.obs") %>%
  corrplot.mixed(order = "FPC", diag = "n", outline = "gray")
```

@@

zoom_soh %>% dplyr::select(Zoom, "G*" = UpZoom) -> y1
zoom_soh %>% dplyr::select(Zoom, "Focal G*" = UpFocalZoom) -> y2

@@

zoom_soh %>% dplyr::select(Zoom, "G*" = DownZoom) -> y1
zoom_soh %>% dplyr::select(Zoom, "Focal G*" = DownFocalZoom) -> y2

@@

```{r weight, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
d3 <- read.csv("data/w_focal_trued3.csv")
d3global <- read.csv("data/w_focal_falsed3.csv")

mean <- aggregate(d3$Up, by = list(d3$W + 4), mean)
sd <- aggregate(d3$Up, by = list(d3$W + 4), sd)
meanG <- aggregate(d3global$Up, by = list(d3global$W + 4), mean)
sdG <- aggregate(d3global$Up, by = list(d3global$W + 4), sd)

plot(NA,
     ylab = expression(SoH^Up),
     xlab = sprintf("Weight matrix size"),
     xlim = c(7,43), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))

mean <- aggregate(d3$Down, by = list(d3$W + 4), mean)
sd <- aggregate(d3$Down, by = list(d3$W + 4), sd)
meanG <- aggregate(d3global$Down, by = list(d3global$W + 4), mean)
sdG <- aggregate(d3global$Down, by = list(d3global$W + 4), sd)

plot(NA,
     ylab = expression(SoH^Down),
     xlab = sprintf("Weight matrix size"),
     xlim = c(7,43), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*", "G*") , fill = c("red", "blue"))

```

```{r aggregation, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}
d3 <- read.csv("data/a_focal_trued3.csv")
d3global <- read.csv("data/a_focal_falsed3.csv")

mean <- aggregate(d3$Up, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Up, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Up, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Up, by = list(d3global$Z + 1), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))

mean <- aggregate(d3$Down, by = list(d3$Z + 1), mean)
sd <- aggregate(d3$Down, by = list(d3$Z + 1), sd)
meanG <- aggregate(d3global$Down, by = list(d3global$Z + 1), mean)
sdG <- aggregate(d3global$Down, by = list(d3global$Z + 1), sd)
plot(NA, 
     ylab = expression(SoH^Down),
     xlab = sprintf("Aggregation levels"),
     xlim = c(2,6), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
plotCI(x = meanG$Group.1,
       y = meanG$x,
       uiw = sdG$x, err = "y", pch = 20, slty = 3, scol = "blue", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
lines(meanG$Group.1, meanG$x, col = "blue", lw = 4)
legend("topleft", c("Focal G*","G*") , fill = c("red","blue"))
```

```{r focal, echo=FALSE, eval=TRUE, cache=TRUE, message=FALSE}

d3 <- read.csv("data/f_focal_trued3.csv")

mean <- aggregate(d3$Up, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Up, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Up),
     xlab = "Focal matrix size",
     xlim = c(29, 137), ylim = c(0, 1))
plotCI(x = mean$Group.1, y = mean$x, uiw = sd$x, err = "y", pch = 20, slty = 3,
       scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))

mean <- aggregate(d3$Down, by = list(d3$F + 12), mean)
sd <- aggregate(d3$Down, by = list(d3$F + 12), sd)
plot(NA,
     ylab = expression(SoH^Down),
     xlab = "Focal matrix size",
     xlim = c(29,137), ylim = c(0,1))
plotCI(x = mean$Group.1,
       y = mean$x,
       uiw = sd$x, err = "y", pch = 20, slty = 3, scol = "red", add = TRUE)
lines(mean$Group.1, mean$x, col = "red", lw = 4)
legend("topleft", c("Focal G*") , fill = c("red"))

```
